This is an example of article title

### 2019-08-29 paper.tex
"generate" header.tex by hand

\begin{lstlisting}
# assuming session was started with many julia workers

@@

d_observations = distribute(observations, 8) # distribute into 8 parts, equally split between available julia processes
d_minutely = groupreduce(Mean(Measurement{Float64}), d_observations,
                         :time => t->trunc(t, Minute), select=:x)

>>>>

\begin{lstlisting}
# assuming Julia session was started with many julia workers

@@

# distribute into 8 parts, equally split
# between available julia processes
d_observations = distribute(observations, 8)
d_minutely = groupreduce(Mean(Measurement{Float64}),
                         d_observations,
                         :time => t->trunc(t, Minute),
                         select=:x)
